Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
block location figures from running

## Tweets location pre-debate 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}

@@

## Tweets location post-debate 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}

>>>>

## Tweets location pre-debate 
```{r, eval=FALSE, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}

@@

## Tweets location post-debate 
```{r, eval=FALSE, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
